MSK III

### 2017-07-18 msk3.rmd
added main case and added linkurl to be blue

---
title: "MSK III"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
---

@@

## Developmental dysplasia of the hip

@@

>>>>

---
title: "MSK III"
author: "Aaron Khoo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  pdf_document
documentclass: article
classoption: a4paper
urlcolor: blue
---

@@

## Developmental dysplasia of the hip (DDH)

@@

## Trigger 1

> 32M, crossfit 4/12, sudden sharp pain in groin

DDx groin pain:

-  CVS: avascular necrosis, 
-  Resp: 
-  MSK: muscle strain, tendonitis, trochanteric bursitis, overuse injury, fracture, labral tear, ligamentous injury, 
-  GIT: bowel obstruction
-  Neuro: nerve impingement
-  Genitourinary: kidney stones, testicular torsion, ovarian cyst
-  Lymphadenopathy, cellulitis

Anatomical structures referring pain: knee, back, hip, intraabdominal = {repro, kidneys}

Questions to ask: also about shooting/numbness/sharp or stabbing/...

## Trigger 2

Catching = joint, giving way under him = ligamentous

[RACGP article on hip pain](http://www.racgp.org.au/afp/2014/april/hip-pain-in-young-adults/)

## Trigger 3

If worried about adductor pain: can use adductor squeeze.

Imaging:

-  X-ray: only see bone
-  CT: loads of radiation
-  Ultrasound:
-  MRI: lots of soft tissue, fractures

## Trigger 4

Ix:

-  Bloods: FBC, 
-  More imaging

Hip impingement:

-  CAM lesion: non-smooth (aspherical) femoral head: 14% in normal population.
-  Pincer: non-smooth acetabulum
-  Combined: both CAM and pincer

Prognosis:

-  Increased risk of OA

## Trigger 5

Arthrogram: injection of contrast followed by MRI. Allows intraarticular structures such as cartilage to be found. Risks = {anaphylaxis, infn, hitting a nerve}. Doubles sensitivity compared to normal MRI without arthrogram (0.60).

Labral tears are common, often asymptomatic.

Mx:

-  Rest
-  NSAIDs
-  Activity modification
-  Physiotherapy exercises
-  Arthroscopy
-  Debridement of bone

## Trigger 6

Physio exercises
